---
title: "Challenge-5"
author: "Sherica Chua"
date: "13/09/2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 


```{r, eval=FALSE,echo=TRUE}
library(tidyverse)
```
**Solutions:**

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

```{r, eval=TRUE,echo=TRUE}

x <-5
function_1 <- function() {
  
  x <- 10
  print(x)
}

print(x)
function_1()
  
```


<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}

total <- 3
function_2 <- function(x) {
  total <<- x + total
}

function_2(10)
print(total)
function_2(5)
print(total)
function_2(33)
print(total)
```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
total = 100
add<-3

new_total <- function(add) {
  
  total <<- add + total
}

new_total(3)
total

```
<br>

#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}

outer_function <- function() {
  
  x <- 5
  inner_function <- function() {
    print(x)
  
  }
  inner_function()
}

outer_function()

```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
library(magick)
str(magick::magick_config())

Meme <- function(path) {
  frink<-image_read(path)
image_annotate(frink, "CONFIDENTIAL", size = 30, color = "red", boxcolor = "pink",
  degrees = 60, location = "+50+100")
}

Meme("https://jeroen.github.io/images/frink.png")


```


```
<br>

#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user inputs a sentence, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**

```{r, eval=FALSE,echo=TRUE}

text_analysis_game <- function() {
  
  cat("Welcome to the Text Analysis Game!\n")
  sentence <- readline(prompt = "Enter a sentence: ")
  
 
  words <- strsplit(sentence, " ")[[1]]
  num_words <- length(words)
  num_chars <- nchar(sentence)
  avg_word_length <- num_chars / num_words
  
  
  cat("\nText Statistics:\n")
  cat("Number of words:", num_words, "\n")
  cat("Number of characters:", num_chars, "\n")
  cat("Average word length:", round(avg_word_length, 2), "\n")
  
  ifelse(avg_word_length < 4, skill_level <- "Novice Communicator",ifelse(avg_word_length < 6,skill_level <- "Intermediate Communicator",skill_level <- "Advanced Communicator"))
  
  cat("\nCommunication Skill Level:", skill_level, "\n")
}


text_analysis_game()

```
<br>